\plaintitle

### 2017-06-21 papers/IoT2017/analysis.tex
final

\subsection{Safety}
We now demonstrate that faulty or malicious prosumers cannot trade
excessive amounts of energy if normal prosumers follow the rules of
the trading workflow.  First, we can show that the net amount of
energy sold by prosumer $i$ for each timestep is at most
$\field{MAXEPA}_i$.  By definition, \textcolor{blue}{we assume that the smart meters enforce a constraint, which ensures that} the amount of energy sold is less
than or equal to the amount of EPA obtained by prosumer $i$.

A prosumer can obtain EPA either by withdrawing from its smart meter
or by purchasing form another prosumer.  From its smart meter,
prosumer $i$ can withdraw at most $\field{MAXEPA}_i$.  Although the
prosumer may also buy EPA from another prosumer, this constitutes
buying energy, which decreases the net amount of energy sold with the
same amount.  Hence, the net amount of energy sold by prosumer $i$
cannot exceed $\field{MAXEPA}_i$.  By extending the argument, we can
show that the net amount of energy sold by a group of prosumers~$G$
cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, %we can
%show that
 the net amount of energy bought by a group of prosumers $G$
cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.

>>>>

\subsection{Safety}
We now demonstrate that faulty or malicious prosumers cannot trade
excessive amounts of energy if normal prosumers follow the rules of
the trading workflow.  First, we can show that the net amount of
energy sold by prosumer $i$ for each timestep is at most
$\field{MAXEPA}_i$.  Due to the rules of the trading workflow, the gross amount of energy sold is less than or equal to the amount of EPA
obtained by prosumer $i$.
%
A prosumer can obtain EPA either by withdrawing from its smart meter
or by purchasing from another prosumer.  From its smart meter,
prosumer $i$ can withdraw at most $\field{MAXEPA}_i$.  Although the
prosumer may also buy EPA from another prosumer, this constitutes
buying energy, which decreases the net amount of energy sold with the
same amount.  Hence, the net amount of energy sold by prosumer $i$
cannot exceed $\field{MAXEPA}_i$.  By extending the argument, we can
show that the net amount of energy sold by a group of prosumers~$G$
cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, %we can
%show that
 the net amount of energy bought by a group of prosumers $G$
cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.

### 2017-06-21 papers/IoT2017/concl.tex
final

\Doug{Abhishek, as always, it would be best if we could revise this summary of the paper's contents to be a summary of lessons learned based upon our experiences to date!}
As the complexity of power systems increases due to the evolution of
power grids, decentralized transactive-energy IoT systems are emerging
to tackle this complexity. Ironically, these decentralized systems
also give rise to new privacy challenges, such as leakage of energy usage patterns, including the possibility of inference of future state of a prosumer, 
\Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}
which are exacerbated by the stringent safety and
security requirements of power systems.

This paper describes how we address these challenges via
\emph{Privacy-preserving Energy Transactions} (PETra), which is our
innovative solution for anonymous energy trading within a transactive
microgrid.  PETra builds on distributed ledgers, such as blockchains,
and proven techniques for anonymity, such as mixing services and onion
routing.  We described the workflow of anonymous energy trading and
explained the novel transactions and services used in PETra.  Finally,
we discussed how PETra satisfies security, safety, and privacy
requirements.  In future work, we will provide rigorous proofs of
satisfying these requirements.
% and we will present an implementation
%of PETra with performance results.

>>>>

\Doug{Abhishek, as always, it would be best if we could revise this summary of the paper's contents to be a summary of lessons learned based upon our experiences to date!}
As the complexity of power systems increases due to the evolution of
power grids, decentralized transactive-energy IoT systems are emerging
to tackle this complexity. Ironically, these decentralized systems
also give rise to new privacy challenges, such as the potential leakage of energy usage patterns, including the possibility of inferring the future state of a prosumer.
These challenges are exacerbated by the stringent safety and
security requirements of power systems.

This paper describes 
\emph{Privacy-preserving Energy Transactions} (PETra), our
innovative solution for anonymous energy trading within a transactive
microgrid.  PETra builds on distributed ledgers, such as blockchains,
and proven techniques for anonymity, such as mixing services and onion
routing.  We described the workflow of anonymous energy trading and
explained the novel transactions and services used in PETra.  Finally,
we discussed how PETra satisfies security, safety, and privacy
requirements.  In future work, we will provide rigorous proofs of
satisfying these requirements.
% and we will present an implementation
%of PETra with performance results.

### 2017-06-21 papers/IoT2017/intro.tex
final

Furthering the concept of microgrids, transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} on the same
feeder (\emph{i.e.}, those sharing a power line link) can operate in
an open market, trading and exchanging generated energy
locally. \emph{Distribution System Operators} (DSOs) can be the
custodians of this market, while still meeting the net demand
\cite{7462854}. For example, the Brooklyn Microgrid
(\url{brooklynmicrogrid.com}) is a peer-to-peer market for locally
generated renewable energy developed by LO3 Energy as a pilot project.

@@

This paper describes an overview of the transactive sequence between
different components of the systems. We also describe the structure of
these transactions and show how they can be used to provide
\emph{Privacy-preserving Energy Transactions} (PETra). PETra is our
distributed-ledger based solution that (1) enables trading energy
futures in a secure and verifiable manner, (2) preserves prosumer
privacy, and (3) enables DSOs to regulate trading and enforce certain
safety rules.

% \Aron{Since SIGCHI does not have section numbers, this paragraph,
%  which describes the organization of the paper, is not very clear.}
%The remainder of
This paper is organized as follows: we first describe
the basic components of a transactive IoT microgrid and formulate
security, safety, and privacy requirements; we next introduce PETra
and describe the transactions and services used to implement it; we
then discuss how it satisfies the security, safety, and privacy
requirements; finally we 
%compare our work on PETra with 
describe related work
and present concluding remarks.

>>>>

Furthering the concept of microgrids, transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} on the same
feeder (\emph{i.e.}, those sharing a power line link) can operate in
an open market, trading and exchanging generated energy
locally. \emph{Distribution System Operators} (DSOs) can be the
custodians of this market, while still meeting the net demand
\cite{7462854}. For example, the Brooklyn Microgrid
(\url{brooklynmicrogrid.com}) is a peer-to-peer market for locally
generated renewable energy, which was developed by LO3 Energy as a pilot project.

@@

This paper introduces %an overview of the transactive sequence between
%different components of the systems. We also describe the structure of
%these transactions and show how they can be used to provide
\emph{Privacy-preserving Energy Transactions} (PETra), which is our
distributed-ledger based solution that (1) enables trading energy
futures in a secure and verifiable manner, (2) preserves prosumer
privacy, and (3) enables DSOs to regulate trading and enforce certain
safety rules.
%
This paper is organized as follows: we first describe
the basic components of a transactive IoT microgrid and formulate
security, safety, and privacy requirements; we next introduce PETra
and describe the transactions and services used to implement it; we
then discuss how it satisfies the security, safety, and privacy
requirements; finally, we 
%compare our work on PETra with 
describe related work
and present concluding remarks.

### 2017-06-21 papers/IoT2017/paper.tex
update
final

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which arrange local
communities into transactive microgrids.  Within a transactive
microgrid, ``prosumers'' (i.e., consumers with energy generation and
storage capabilities) can trade energy with each other, thereby
smoothing the load on the main grid using local supply.  It is hard,
however, to provide security, safety, and privacy in a decentralized
and transactive energy system.  On the one hand, prosumers' personal
information must be protected from their trade partners and the system
operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes \change{our}{\emph{Privacy-preserving
    Energy Transactions} (PETra)}, which is secure and safe solution
for transactive microgrids that enables consumers to trade energy
without sacrificing their privacy.  \change{Our solution}{PETra}
builds on distributed ledgers, such as blockchains, and provides
anonymity for communication, bidding, and trading.
\end{abstract}

@@

% BALANCE COLUMNS
\balance{}

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{references}

>>>>

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which arrange local
communities into transactive microgrids.  Within a transactive
microgrid, ``prosumers'' (i.e., consumers with energy generation and
storage capabilities) can trade energy with each other, thereby
smoothing the load on the main grid using local supply.  It is hard,
however, to provide security, safety, and privacy in a decentralized
and transactive energy system.  On the one hand, prosumers' personal
information must be protected from their trade partners and the system
operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.  This paper describes \emph{Privacy-preserving
    Energy Transactions} (PETra), which is a secure and safe solution
for transactive microgrids that enables consumers to trade energy
without sacrificing their privacy.  PETra
builds on distributed ledgers, such as blockchains, and provides
anonymity for communication, bidding, and trading.
\end{abstract}

@@

% BALANCE COLUMNS
%\balance{}
%\setlength{\bibsep}{0pt plus 0ex}
%\let\oldthebibliography\thebibliography
%\let\endoldthebibliography\endthebibliography
%\renewenvironment{thebibliography}[1]{
%  \begin{oldthebibliography}{#1}
%    \setlength{\itemsep}{0.1em}
%    \setlength{\parskip}{0em}
%}
%{
%  \end{oldthebibliography}
%}

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}

\bibliography{references}

### 2017-06-21 papers/IoT2017/solution.tex
updates
final

This section describes \emph{Privacy-preserving Energy Transactions}
(PETra), which is our solution for providing privacy to prosumers in a
transactive energy IoT system, without compromising grid safety and
security.
\begin{figure*}[h]
\centering
\begin{tikzpicture}[x=3.8cm, y=1.6cm, font=\small,
  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
  entity/.style={draw, align=center, rounded corners=0.1cm},
  asset/.style={midway, align=center},
  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
]
\node[entity] (smartmeter) at (0, 1) {smart meter};
\node[entity] (prosumer1) at (1, 1) {prosumer};
\node[system] (mixing1) at (1.9, 1) {mixing\\service};
\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
\node[entity] (partner) at (3, 0) {other prosumer};
\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, above] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified Overview of the Flow of Assets from the Perspective of a Prosumer Who Sells Energy.}
\label{fig:sellFlow}
\end{figure*}

@@

\subsubsection{Energy Selling Workflow}
Consider a prosumer who wishes to sell energy to another prosumer, as
shown in Figure~\ref{fig:sellFlow}\footnote{To prevent
  de-anonymization, a prosumer should use multiple addresses and
  multiple rounds of mixing, which we have omitted from the figure for
  clarity of presentation.}  \Abhishek{We need to mention what is the
  expected deadline by which this sequence of task should finish.}  As
its first step, the prosumer withdraws an \emph{energy production
  asset} from its smart meter.  An energy production asset represents
a permission to sell a certain amount of energy, and it is used to
enforce safety requirements.  If the prosumer has sufficient unsold
production capacity, the smart meter creates and transfers a
production asset to the prosumer using a \emph{smart meter
  transaction} \circled{1}, which is recorded on the distributed
ledger.

@@

The prosumer can now engage in energy trading anonymously.  To find a
trade partner, it can either post an \emph{energy ask} on the bid
storage, or simply search the storage for an acceptable \emph{energy
  bid}.  To post an energy ask, the prosumer first proves to the
storage service---without revealing its original identity---that it
owns a production asset stored at an anonymous address.  Proving
ownership prevents the prosumer from ``spamming'' the storage service
with bogus asks.  The prosumer can then post the energy ask
\circled{4}, which contains an anonymous communication
identifier\footnote{We discuss communication anonymity later.}, a
price, and a reference to the production asset.  If another prosumer,
who is seeking to buy energy, finds the ask acceptable it can contact
the seller using the communication identifier included in the ask.

>>>>

This section describes \emph{Privacy-preserving Energy Transactions}
(PETra), which is our solution for providing privacy to prosumers in a
transactive energy IoT system, without compromising grid safety and
security.

\begin{figure*}[h]
\centering
\begin{tikzpicture}[x=3.8cm, y=1.6cm, font=\small,
  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
  entity/.style={draw, align=center, rounded corners=0.1cm},
  asset/.style={midway, align=center},
  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
]
\node[entity] (smartmeter) at (0, 1) {smart meter};
\node[entity] (prosumer1) at (1, 1) {prosumer};
\node[system] (mixing1) at (1.9, 1) {mixing\\service};
\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
\node[entity] (partner) at (3, 0) {other prosumer};
\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, above] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
Note that to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing, which we have omitted from the figure for clarity of presentation.}
\label{fig:sellFlow}
%\vspace{-0.1in}
\end{figure*}

@@

\subsubsection{Energy Selling Workflow}
Consider a prosumer who wishes to sell energy to another prosumer, as
shown in Figure~\ref{fig:sellFlow}.  \Abhishek{We need to mention what is the
  expected deadline by which this sequence of task should finish.}  As
its first step, the prosumer withdraws an \emph{energy production
  asset} from its smart meter.  An energy production asset represents
a permission to sell a certain amount of energy, and it is used to
enforce safety requirements.  If the prosumer has sufficient unsold
production capacity, the smart meter creates and transfers a
production asset to the prosumer using a \emph{smart meter
  transaction} \circled{1}, which is recorded on the distributed
ledger.

@@

The prosumer can now engage in energy trading anonymously.  To find a
trade partner, it can either post an \emph{energy ask} on the bid
storage, or simply search the storage for an acceptable \emph{energy
  bid}.  To post an energy ask, the prosumer first proves to the
storage service---without revealing its original identity---that it
owns a production asset stored at an anonymous address.  
\Aron{This sentence was added because we removed the relevant safety requirement.}
Proving ownership prevents the prosumer from ``spamming'' the storage service
with bogus asks.  The prosumer can then post the energy ask
\circled{4}, which contains an anonymous communication
identifier\footnote{We discuss communication anonymity later.}, a
price, and a reference to the production asset.  If another prosumer,
who is seeking to buy energy, finds the ask acceptable it can contact
the seller using the communication identifier included in the ask.
